---
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  powerpoint_presentation:
    reference_doc: template_1.pptx
params:
  country: 'Scotland'
  date_1: '2020-03-25'
  date_2: '2020-04-05'
  date_3: '2020-04-26'
title: Mobility reports for `r params$country`
---

```{r setup, include = FALSE, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

date_1 = params$date_1
date_2 = params$date_2
date_3 = params$date_3
amount_to_average_dates = 7

```

```{r prep data, include = FALSE, echo=FALSE, message=FALSE}
#Draw from data sources
library(lubridate)
library(tidyverse)
library(patchwork)
library(rmapshaper)
library(smoothr)

#themes
ggplot_map = function(...) ggplot2::ggplot(...) +
  theme(axis.line=element_blank(),
        axis.text.x=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks=element_blank(),
        axis.title.x=element_blank(),
        axis.title.y=element_text(size = 20, vjust= 5),
        panel.background=element_blank(),
        panel.border=element_blank(),
        panel.grid.major=element_blank(),
        panel.grid.minor=element_blank(),
        plot.background=element_blank(),
        legend.text=element_text(size = 16),
        legend.title=element_blank(),
        plot.title = element_text(size = 22, hjust = 0.45, vjust = 0.5)) + theme(legend.position="bottom") + 
  guides(fill=guide_colourbar(direction = "horizontal", barheight = 0.6, barwidth = 10, frame.colour = 'black'))#+

#download
today_date = lubridate::today()

#Download from google
download.file('https://www.gstatic.com/covid19/mobility/Global_Mobility_Report.csv', 
               destfile = paste0('reports/google/google_', today_date, '_mobility_report.csv'))

#Read the csv file
global_mobility_data = read_csv(paste0('reports/google/google_', today_date, '_mobility_report.csv'))

global_mobility_data = global_mobility_data %>% 
  mutate(sub_region_1 = stringr::str_to_title(sub_region_1),
         sub_region_1 = gsub(' Council', '', sub_region_1),
         sub_region_1 = gsub('Borough Of ', '', sub_region_1),
         sub_region_1 = gsub(' County Borough', '', sub_region_1),
         sub_region_1 = gsub('Na H-Eileanan An Iar', 'Eilean Siar', sub_region_1),
         sub_region_1 = gsub('Wrexham Principal Area', 'Wrexham', sub_region_1))

uk_mobility_data = global_mobility_data %>%
                        filter(country_region_code == 'GB')

uk_mobility_data_national = global_mobility_data %>%
                        filter(country_region_code == 'GB', 
                               is.na(sub_region_1))

uk_mobility_data_subnational = global_mobility_data %>%
                        filter(country_region_code == 'GB', 
                               !is.na(sub_region_1))

#filter for selected dates only

uk_mobility_data_subnational_dates = uk_mobility_data_subnational %>% 
                                     filter(date == date_1 | date == as.Date(date_1) + amount_to_average_dates | date == as.Date(date_1) - amount_to_average_dates |
                                              date == date_2 | date == as.Date(date_2) + amount_to_average_dates | date == as.Date(date_2) - amount_to_average_dates |
                                              date == date_3 | date == as.Date(date_3) + amount_to_average_dates | date == as.Date(date_3) - amount_to_average_dates )

uk_mobility_data_national_dates = uk_mobility_data_national %>% 
                                     filter(date == date_1 | date == date_2 | date == date_3)

#Calculate a lagged average
uk_mobility_data_subnational_dates = uk_mobility_data_subnational_dates %>% 
  mutate(date_diff_1 = ifelse(as.Date(date_1) - date <= amount_to_average_dates & as.Date(date_1) - date >= -amount_to_average_dates, 'Within','Outwith'),
         date_diff_2 = ifelse(as.Date(date_2) - date <= amount_to_average_dates & as.Date(date_2) - date >= -amount_to_average_dates, 'Within','Outwith'),
         date_diff_3 = ifelse(as.Date(date_2) - date <= amount_to_average_dates & as.Date(date_2) - date >= -amount_to_average_dates, 'Within','Outwith')) %>% 
  group_by(sub_region_1, date_diff_1) %>% 
  mutate(residential_percent_change_from_baseline = ifelse(date == date_1, mean(residential_percent_change_from_baseline, na.rm = T),
                                                           residential_percent_change_from_baseline),
         retail_and_recreation_percent_change_from_baseline = ifelse(date == date_1, mean(retail_and_recreation_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           retail_and_recreation_percent_change_from_baseline),
         grocery_and_pharmacy_percent_change_from_baseline = ifelse(date == date_1, mean(grocery_and_pharmacy_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           grocery_and_pharmacy_percent_change_from_baseline),
         parks_percent_change_from_baseline = ifelse(date == date_1, mean(parks_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           parks_percent_change_from_baseline),
         transit_stations_percent_change_from_baseline = ifelse(date == date_1, mean(transit_stations_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           transit_stations_percent_change_from_baseline),
         workplaces_percent_change_from_baseline = ifelse(date == date_1, mean(workplaces_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           workplaces_percent_change_from_baseline)) %>% 
  ungroup() %>% 
    group_by(sub_region_1, date_diff_2) %>% 
  mutate(residential_percent_change_from_baseline = ifelse(date == date_2, mean(residential_percent_change_from_baseline, na.rm = T),
                                                           residential_percent_change_from_baseline),
         retail_and_recreation_percent_change_from_baseline = ifelse(date == date_2, mean(retail_and_recreation_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           retail_and_recreation_percent_change_from_baseline),
         grocery_and_pharmacy_percent_change_from_baseline = ifelse(date == date_2, mean(grocery_and_pharmacy_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           grocery_and_pharmacy_percent_change_from_baseline),
         parks_percent_change_from_baseline = ifelse(date == date_2, mean(parks_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           parks_percent_change_from_baseline),
         transit_stations_percent_change_from_baseline = ifelse(date == date_2, mean(transit_stations_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           transit_stations_percent_change_from_baseline),
         workplaces_percent_change_from_baseline = ifelse(date == date_2, mean(workplaces_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           workplaces_percent_change_from_baseline)) %>% 
    ungroup() %>% 
    group_by(sub_region_1, date_diff_3) %>% 
  mutate(residential_percent_change_from_baseline = ifelse(date == date_3, mean(residential_percent_change_from_baseline, na.rm = T),
                                                           residential_percent_change_from_baseline),
         retail_and_recreation_percent_change_from_baseline = ifelse(date == date_3, mean(retail_and_recreation_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           retail_and_recreation_percent_change_from_baseline),
         grocery_and_pharmacy_percent_change_from_baseline = ifelse(date == date_3, mean(grocery_and_pharmacy_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           grocery_and_pharmacy_percent_change_from_baseline),
         parks_percent_change_from_baseline = ifelse(date == date_3, mean(parks_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           parks_percent_change_from_baseline),
         transit_stations_percent_change_from_baseline = ifelse(date == date_3, mean(transit_stations_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           transit_stations_percent_change_from_baseline),
         workplaces_percent_change_from_baseline = ifelse(date == date_3, mean(workplaces_percent_change_from_baseline, 
                                                                                          na.rm = T),
                                                           workplaces_percent_change_from_baseline)) %>% 
  ungroup() %>% 
                                     filter(date == date_1 |
                                              date == date_2 |
                                              date == date_3) %>% 
  select(-date_diff_1, -date_diff_2, -date_diff_3)

```


```{r prep maps, include = FALSE, echo=FALSE, message=FALSE}
eng_wal_counties_unitary_authorities = geojsonio::geojson_read('geoJSONs/unitary_auth_counties_eng_wal.geojson', what = 'sp')
sco_counties_unitary_authorities = geojsonio::geojson_read('geoJSONs/scotland_la.geojson', what = 'sp')
ni_counties = geojsonio::geojson_read('geoJSONs/ni_counties.geojson', what = 'sp')

#Remove little islands and simplify
eng_wal_counties_unitary_authorities = ms_filter_islands(eng_wal_counties_unitary_authorities, sys = T, min_area = 9999999)
eng_wal_counties_unitary_authorities = ms_simplify(eng_wal_counties_unitary_authorities, sys = T, keep = 0.2)
eng_wal_counties_unitary_authorities = smooth(eng_wal_counties_unitary_authorities, method = 'densify')

sco_counties_unitary_authorities = ms_filter_islands(sco_counties_unitary_authorities, sys = T, min_area = 99999999)
sco_counties_unitary_authorities = ms_simplify(sco_counties_unitary_authorities, sys = T, keep = 0.04)
sco_counties_unitary_authorities = smooth(sco_counties_unitary_authorities, method = 'densify')

ni_counties = ms_filter_islands(ni_counties, sys = T, min_area = 99999999)
ni_counties = ms_simplify(ni_counties, sys = T, keep = 0.1)
ni_counties = smooth(ni_counties, method = 'densify')

#prepare geoJSONs for combining
eng_wal_counties_unitary_authorities$bng_e = NULL
eng_wal_counties_unitary_authorities$bng_n = NULL
eng_wal_counties_unitary_authorities$long = NULL
eng_wal_counties_unitary_authorities$lat = NULL
eng_wal_counties_unitary_authorities$st_areashape = NULL
eng_wal_counties_unitary_authorities$st_lengthshape = NULL
eng_wal_counties_unitary_authorities$details = NULL

ni_counties$id = ni_counties$COUNTY_ID
ni_counties$second_id = ni_counties$OBJECTID
ni_counties$name = ni_counties$CountyName
ni_counties$details = 'Northern Ireland'

ni_counties$COUNTY_ID = NULL
ni_counties$OBJECTID = NULL
ni_counties$CountyName = NULL
ni_counties$Area_SqKM = NULL

names(sco_counties_unitary_authorities) = c('id', 'second_id', 'name', 'details')

sco_counties_unitary_authorities$details = 'Scotland'

names(eng_wal_counties_unitary_authorities) = c('id', 'second_id', 'name', 'details')

eng_sco_wal = rbind(sco_counties_unitary_authorities, eng_wal_counties_unitary_authorities)

eng_sco_wal_ni = rbind(eng_sco_wal, ni_counties)

#make the names correct/ line up with google
eng_sco_wal_ni$name %>% 
  tibble(name = .) %>%
  mutate(name = stringr::str_to_title(name),
         name = gsub('Londonderry', 'Derry And Strabane', name),
         name = gsub(', City Of', '', name),
         name = gsub(', County Of', '', name),
         name = gsub('Borough Of ', '', name),
         name = gsub('Orkney Islands', 'Orkney', name),
         name = gsub('City Of Edinburgh', 'Edinburgh', name),
         name = gsub('Bristol', 'City Of Bristol', name),
         name = gsub('Armagh', 'Armagh City And Banbridge And Craigavon', name)) -> location_eng_sco_wal_ni

eng_sco_wal_ni$name = location_eng_sco_wal_ni$name

unmatched_locations = read_csv('unmatched_names.csv') 

eng_sco_wal_ni@data %>% 
  select(name, details) %>%
  left_join(unmatched_locations, by = 'name') %>% 
  mutate(merge_name = name) %>% 
  mutate(name = ifelse(is.na(new_name), name, new_name)) %>% 
  left_join(uk_mobility_data_subnational_dates, by = c('name' = 'sub_region_1')) %>% 
  dplyr::select(-new_name) -> uk_mobility_data_subnational_dates

if(params$country == 'UK'){
  line_plot_data = uk_mobility_data_national
  uk_mobility_data_subnational_dates = uk_mobility_data_subnational_dates %>%  select(-details)
} else if (params$country == 'Scotland' | params$country == 'England' | params$country == 'Wales' | params$country == 'Northern Ireland'){
    uk_mobility_data_subnational_dates = uk_mobility_data_subnational_dates %>% subset(details == params$country) %>%  select(-details)
    eng_sco_wal_ni = eng_sco_wal_ni %>% subset(details == params$country)
    line_plot_data = uk_mobility_data_subnational %>% filter(sub_region_1 %in% eng_sco_wal_ni$name) %>% 
      group_by(country_region, date) %>% 
      summarise(retail_and_recreation_percent_change_from_baseline = mean(retail_and_recreation_percent_change_from_baseline, na.rm = T),
                grocery_and_pharmacy_percent_change_from_baseline = mean(grocery_and_pharmacy_percent_change_from_baseline, na.rm = T),
                parks_percent_change_from_baseline = mean(parks_percent_change_from_baseline, na.rm = T),
                transit_stations_percent_change_from_baseline = mean(transit_stations_percent_change_from_baseline, na.rm = T),
                residential_percent_change_from_baseline = mean(residential_percent_change_from_baseline, na.rm = T),
                workplaces_percent_change_from_baseline = mean(workplaces_percent_change_from_baseline, na.rm = T)) %>% drop_na()
}

```

```{r combine data, include = FALSE, echo=FALSE, message=FALSE}
uk_mobility_data_subnational_dates = uk_mobility_data_subnational_dates %>% 
  mutate(date_class = ifelse(date == date_1, '1', NA),
         date_class = ifelse(date == date_2, '2', date_class),
         date_class = ifelse(date == date_3, '3', date_class)) %>% 
  select(-name, -country_region_code, -country_region, -sub_region_2) %>% 
  pivot_wider(names_from = date_class, 
              values_from = all_of(c("date", "retail_and_recreation_percent_change_from_baseline", "grocery_and_pharmacy_percent_change_from_baseline", 
                                                             "parks_percent_change_from_baseline", "transit_stations_percent_change_from_baseline",
                                                             "workplaces_percent_change_from_baseline", "residential_percent_change_from_baseline" 
                                                             ))) %>% 
  select(-contains('_NA', ignore.case = FALSE))

  uk_mobility_data_sp = uk_mobility_data_subnational_dates %>% 
  sp::merge(eng_sco_wal_ni, ., by.x = 'name', by.y = 'merge_name')
```

## `r params$country` Mobility Reports

This is a report from mobility data recorded by Google. It reports percentage change by region compared to the baseline level of movements.

Reports represent movement from several days ago (as data has to be aggregated by google). The most recent available data was released `r as.Date(max(na.omit(uk_mobility_data_national$date))) %>% format('%d %B, %Y')`.

Report generated `r format(Sys.time(), '%d %B, %Y')`.

## Change in Residential Mobility

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'residential_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Residential'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("#e89f00", "white", "blue"), values = c('0', '0.25', '0.5', '0.75', '1'), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-50,50), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours =rev(c("#0e1b76", "white", "#e89f00")), values = c(0, 0.25, 0.50, 0.75, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(-50,50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = 15), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```

## Retail and Recreation

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'retail_and_recreation_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Retail'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "white", "red"), values = c(0, 0.25, 1), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-100,0), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
  mutate(date_1_to_3 = ifelse(date_1_to_3 < 0, 0, date_1_to_3)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "#e89f00"), values=c(0, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(0, 50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = -40), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```


## Pharmacy and Groceries

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'grocery_and_pharmacy_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Pharmacy and Groceries'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
  mutate(var_1 = ifelse(var_1 > 0, 0, var_1)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "white", "red"), values = c(0, 0.25, 1), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-100,0), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
    mutate(date_1_to_3 = ifelse(date_1_to_3 < 0, 0, date_1_to_3)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "#e89f00"), values=c(0, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(0, 50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = -20), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```





## Transit

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'transit_stations_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Transit'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
    mutate(var_1 = ifelse(var_1 > 0, 0, var_1)) %>%
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "white", "red"), values = c(0, 0.25, 1), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-100,0), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
  mutate(date_1_to_3 = ifelse(date_1_to_3 < 0, 0, date_1_to_3)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "#e89f00"), values=c(0, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(0, 50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = -35), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```


## Parks

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'parks_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Parks'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "white", "red"), values = c(0, 0.25, 1), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-100,0), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "#e89f00"), values=c(0, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(-50, 50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = -15), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```


## Workplace

```{r fig.width=30, fig.height=17.5, echo=FALSE, message=FALSE}
chunk_var = 'workplaces_percent_change_from_baseline'
chunk_map_text = 'Hello'
chunk_map_y_lab = 'Parks'

chunk_data_sp = uk_mobility_data_sp

var_1 = paste0(chunk_var, '_1')
var_2 = paste0(chunk_var, '_2')
var_3 = paste0(chunk_var, '_3')

test = chunk_data_sp@data

chunk_data_sp@data = chunk_data_sp@data %>% 
  select(name, id, second_id, details, date_3, date_2, date_1, contains(chunk_var)) %>% 
  mutate(date_1_to_3 := !!as.name(var_3) - !!as.name(var_1),
         date_2_to_3 := !!as.name(var_3) - !!as.name(var_2),
         date_1_to_2 := !!as.name(var_2) - !!as.name(var_1))                            

#fortify
chunk_data_sp_points = fortify(chunk_data_sp, region = "id")
chunk_data_sp_fort = dplyr::left_join(chunk_data_sp_points, chunk_data_sp@data, by="id")

#plot the first date only
fixed_baseline_plot = chunk_data_sp_fort %>% 
  mutate(var_1 = ifelse(var_1 > 0, 0, var_1)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = var_1), size = 0.25, color = 'black') + coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "white", "red"), values = c(0, 0.25, 1), 
                       breaks = 50*-2:2, labels =  50*-2:2, limits = c(-100,0), name = chunk_map_text) + 
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(as.Date(date_1) %>% format("%d-%B-%Y"))

# #plot difference between first and third date
change_plot = chunk_data_sp_fort %>%
  mutate(date_1_to_3 = ifelse(date_1_to_3 < 0, 0, date_1_to_3)) %>% 
  ggplot_map(aes(y = lat, x = long, group = group)) + geom_polygon(aes_string(fill = 'date_1_to_3'), size = 0.25, color = 'black') + 
  coord_equal(ratio = 1.3) +
  scale_fill_gradientn(colours = c("white", "#e89f00"), values=c(0, 1), breaks = 50*-2:2, 
                       labels =  50*-2:2, limits = c(0, 50), name = chunk_map_text) +
  ylab(chunk_map_y_lab) + theme(axis.title.y = element_blank()) +
  ggtitle(paste0(as.Date(date_1) %>% format("%d-%b-%Y"), ' to ', as.Date(date_3) %>% format("%d-%b-%Y")))

#Plot line change
plot_line_change = line_plot_data %>% 
  ggplot(aes(x = date)) + 
  geom_vline(xintercept = as.Date('2020-03-21'), colour="dark grey", size = 1, linetype = 'dashed') +
  geom_text(aes(x= as.Date('2020-03-21'), label="Restrictions\nImposed", y = -35), colour="grey", angle=90, size = 5) +
  geom_path(aes_string(y = chunk_var), size = 1.8, colour = '#454545') +
  geom_point(aes_string(y = chunk_var), size = 4, colour = '#00acac') + theme_minimal() + xlab('Date') + 
  ylab('Change from\nBaseline (%)') + ylim(min(uk_mobility_data_national[chunk_var]) - 2,
                                      max(uk_mobility_data_national[chunk_var]) + 5) + 
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(size = 20),
        axis.title.y = element_text(size = 20, vjust = 5),
        axis.text.y = element_text(size = 18),
        plot.margin = unit(c(1,1,1,1),"cm"))

(fixed_baseline_plot | change_plot) / plot_line_change +  plot_layout(heights = unit(c(35, 4), c('cm', 'cm')), widths = unit(c(40, 12), c('cm', 'cm'))) 

rm(chunk_var, plot_line_change, chunk_data_sp, var_1, var_2, var_3)
```