---
title: "UK Mobility Reports"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  powerpoint_presentation:
    reference_doc: template_1.pptx

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
load('continuous_plots.RData')
library(tidyverse)
library(patchwork)
```

## UK Mobility Reports

This is a report from mobility data recorded by Google. It reports percentage change by region compared to the baseline level of movements.

Reports represent movement from several days ago (as data has to be aggregated by google). The most recent available data was released on `r date_of_pull`.

## Residential Movements 

```{r fig.width=25, fig.height=10, echo=FALSE}
(c1 + ggtitle(date_of_pull) | scotland_c_1)
```

## Pharmacy/ Groceries Movements

```{r fig.width=25, fig.height=10, echo=FALSE}
(c2 + ggtitle(date_of_pull) | scotland_c_2)
```

## Transit Movements

```{r fig.width=25, fig.height=10, echo=FALSE}
(c3 + ggtitle(date_of_pull) | scotland_c3)
```

## Residential Movements 

```{r fig.width=25, fig.height=10, echo=FALSE}
(c4 + ggtitle(date_of_pull) | scotland_c4)
```

## Park Movements

```{r fig.width=25, fig.height=10, echo=FALSE}
(c5 + ggtitle(date_of_pull) | scotland_c5)
```

## Workplace Movements

```{r fig.width=25, fig.height=10, echo=FALSE}
(c6 + ggtitle(date_of_pull) | scotland_c6)
```
